The impact of cosmic variance on constraining the mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z \sim 3$

### 2014-04-03 paper/ms.tex
new reference + simulation section

The Bolshoi simulation \citep{Bolshoi} we use in this paper was
performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. The
dark matter distribution is sampled using $2048^{3}$ particles, which
translates into a particle mass of $m_{\rm p}=1.35\times 10^{8}$
$h^{-1}$ M$_{\odot}$.  The cosmological parameters are consistent with
a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$,
cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant
$h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the
power spectrum$\sigma_{8}=0.82$ \citep{Komatsu2009,Jarosik2011}.

We use halo catalogs constructed with a Friend-of-Friends (FOF)
algorithm with a linking length of 0.17 times the inter-particle
distance. The catalogs were obtained from the publicly available
Multidark database \footnote{{\tt
    http://www.multidark.org/MultiDark/}}
\citep{MultiDark}. For each halo in the box we store its
comoving position in the box (3-D coordinates) and FOF mass. We focus our work
on halos more massive than $1\times 10^{10}$\hMsun that are resolved
with at least $70$ particles, the reasons for this choice are
explained in the next sub-section.

>>>>

We use results form the Bolshoi simulation \citep{Bolshoi} which
was performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side. The
dark matter distribution is sampled using $2048^{3}$ particles. The
cosmological parameters are consistent with a Wilkinson Microwave
Anisotropy Probe (WMAP) ninth year data with a matter density
$\Omega_{\rm m} = 0.27$, cosmological constant
$\Omega_{\Lambda}=0.73$, dimensionless Hubble constant $h=0.70$, slope
of the power spectrum $n=0.95$ and normalization of the power
spectrum$\sigma_{8}=0.82$ \citep{hinshaw_etal13}.   This
translates into a particle mass of $m_{\rm p}=1.35\times 10^{8}$
$h^{-1}$ M$_{\odot}$.

We use halo catalogs constructed with a Friend-of-Friends (FOF)
algorithm with a linking length of 0.17 times the inter-particle
distance. The catalogs were obtained from the publicly available
Multidark database \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{MultiDark}. For each
halo in the box we store its comoving position in the box (3-D
coordinates) and FOF mass. We focus our work on halos more massive
than $1\times 10^{10}$\hMsun resolved with at least $70$ particles.
%the reasons for this choice are explained in the next sub-section.
